\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-15 paper/paper.tex
save

@@

\begin{table*}[htb]
    \begin{tabular}[htb]{l|l|l|l}
    Try & Normal               & Random (slower than best) & Random (faster than best) \\ \hline
    1   & Best throughput      & Best throughput           & Random                    \\
    2   & Next best throughput & Random                    & Best throughput           \\
    3   & Highest probability  & Highest probability       & Highest probability       \\
    4   & Lowest rate          & Lowest rate               & Lowest rate               \\
    \end{tabular}
    \caption{Multi-rate retry chains for Minstrel}
\label{table:1}
\end{table*}

@@

@@

\begin{figure}[htb]
  \hspace{-.75em}\includegraphics[width=3.5in]{constant.png}\vspace{-0em}
  \caption{Throughput of using a constant 802.11b/g bitrate in an MIT basement.}
\end{figure}

@@

Harness.py, etc.

@@

Minstrel actually is better than SampleRate (except on short traces). Eit.

@@

@@

The end.

>>>>

\date{May 2013}

@@

\begin{table*}[htb]
  \centering
    \begin{tabular}[htb]{l|l|l|l}
    Try & Normal               & Random (slower than best) & Random (faster than best) \\ \hline
    1   & Best throughput      & Best throughput           & Random                    \\
    2   & Next best throughput & Random                    & Best throughput           \\
    3   & Highest probability  & Highest probability       & Highest probability       \\
    4   & Lowest rate          & Lowest rate               & Lowest rate               \\
    \end{tabular}
    \caption{Multi-rate retry chains for Minstrel}
\label{table:1}
\end{table*}

@@

TODO

@@

@@

TODO: Harness.py, etc.

@@

Minstrel and SampleRate perform similarly. Minstrel sometimes has very poor performance on short traces--as low as 2mbps. This is because it does not stop sending after four successive failures, but must wait until the end of the 100ms window for statistics to be compiled.

\begin{figure}[htb]
  \hspace{-1em}\includegraphics[width=3.4in]{constant.png}\vspace{-0em}
  \caption{Throughput of using a constant 802.11b/g bitrate in clear line-of-sight from the access point.}
\end{figure}

\begin{figure}[htb]
  \hspace{-.75em}\includegraphics[width=3.5in]{MinVSSam1.png}\vspace{-0em}
  \caption{Throughput of Minstrel and SampleRate on various trace situations.}
\end{figure}

@@

\begin{figure}[htb]
  \hspace{-2em}\includegraphics[width=3.5in]{mnVSspVSmp1.png}\vspace{-0em}
  \caption{Throughput of Minproved as compared to SampleRate and vanilla Minstrel.}
\end{figure}

@@

Minstrel and SampleRate perform similarly. The results suggest that SampleRate tends to do slightly better, except in very lossy links such as the client being far awat from the AP or actively moving. Minproved, our improved version of Minstrel, solidly outperforms both Minstrel and SampleRate.

It seems like the abandonment of SampleRate in the Linux kernel may have been a bit hasty, since it seems to perform similarly to Minstrel and it is a much simpler algorithm and thus less bug prone. We are not sure if there are adjustments to SampleRate that will bring it's performance near Minproved, though.
